### 2024-08-11 doc/Thesis/chapter/03-experimental.tex
correct misspellings

\section{Substrate Preparation}
Five different substrates were used throughout this work: 
1 mm-thick, soda-lime microscope glass slides 
%\linebreak[4] 
(\cm{2.5}$\times$\cm{7.5}) from Sigma Aldrich, thinner, 
squared glass plates (\cm{2.5}\x\cm{2.5}) Menzel Gläser,
\gls{ito} coated glass (\cm{2.5}\x\cm{2.5}) from Sigma Aldrich with a sheet resistance of approximately 12 $\Omega$/sq, 
\gls{fto} coated glass (\cm{5}\x\cm{5}) from Sigma Aldrich and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%
The steel foil was cut with a foil cutter into \cm{2.5}\x\cm{2.5} squares.
Glass was used because of its low price point and availability and to measure transmission and reflectance spectra. 
\Gls{fto} and \gls{ito} coated conducting substrates were used for \gls{sem} investigation and for electrical measurements (serving as one of the electrical contacts).
%\gls{fto} and \gls{ito} were used in order to have a conducting substrate. 
%, which is needed to measure the conductivity of the applied layer and \td{for \gls{sem} micrographs. (don't follow?)}
The conducting substrate allows for easy measurement of electric conductance in vertical direction.
Furthermore, while taking a \gls{sem} micrograph the sample would quickly accumulate negative charge and repell further electrons without a conducting substrate.
%The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
%The steel foil was cut with a foil cutter into squares of the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in a ultrasonic bath
	\item \minutes{15} in \gls{water} in a ultrasonic bath
	\item \minutes{15} in \gls{ipo} in a ultrasonic bath 
\end{enumerate}
%\td{is that the usual procedure for steel?}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the coating step (cf. \cite{YAMASHITA2018,Kohli2010}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Aqueous Precursor Solutions}
\label{sec:exp-sol-aq}
\gls{zrpro} was added to acetylacetone (\gls{acac}) while stirring and in a separate vessel \gls{water} 
(including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
was added to isopropyl aclohol (\gls{ipo}) and both were stirred for one hour. 
These additives were added to influence pH and surface tension with the goal to influence the homogeneity of the resulting layer. %(in terms of what?)}. % \td{see Parvulescu2015}
The \gls{water}-\gls{ipo} mixture was added to the \gls{zrpro}-gls{acac} solution and stirred over night. 
The exact volumes can be taken from table~\ref{tab:rec1}.
%Unfortunately, this solution failed to produce \td{anything near homogeneous layers (??)}.
Unfortunately, this solution failed to produce homogeneous layers, but instead only resulted in sparse patches of deposits on the substrate.
Thus, an alternative solution was found.
%\td{At this point in time everything was doctor bladed by hand. The hight was varied (with tape).}
\begin{table}[h]
	\centering
	\caption{Compositions of different aqueous solutions}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
		\hline
		\gls{zrpro} [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac}  [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo}   [\ml{}]	&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [\ml{}]	&2.6	&2.6	&2.5	&2~		&2		&2		&2\\
		\gls{sds}   [\mg{}]	&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl}   [\ml{}]	&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [\ml{}]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh}  [\ml{}] &-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Buthanolic Solution}\label{sec:exp-sol-bu}
%\todo{what did you did you do percisely! It must be logical and should be followed}
Five different concentrations of the buthanolic solutions were prepared.
\ds{
\td{Not all (which?)} chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
starting materials had to be chosen from the available inventory. 
}
The base recipe (\gls{1f}) was inspired by Hu~et~al.\cite{Hu2016}.
\Gls{buoh}, \gls{zrpro}, \gls{acac} and \gls{ipo}/\gls{acoh} were used as solvent, precursor, chelating agent and stabilization agent, respectively.

@@

\begin{table}[h]
	\centering
    \caption{Heating programs}
	\label{tab:heating}
	\begin{subtable}{\textwidth}
		\centering
		\subcaption{Heating program HP1 used with the Labtech EH45C heating plate}
		\label{tab:labtech}
%		\begin{tabular}{rl ll ll ll ll ll ll }%ll ll ll ll ll ll ll}
		\begin{tabular}{cc cc cc cc cc cc cc }%ll ll ll ll ll ll ll}
			\hline
			\hline
			T [\oc{}]	    &80		&100	&150	&160	&170 	&180	&190	&200	&250	&300	&350	&400	\\
			\hline
			t [\minutes{}]	&10 	&10		&5 		&5 		&5 		&5 &5 &10 &10 &10 &10 &60 \\
			\hline
			\hline
		\end{tabular}
	\end{subtable}
%%%%%%%%%%%%
	\begin{subtable}{\textwidth}
		\centering
		\subcaption{Heating programs NT1 - NT6 used with the Naberterm LB410 muffle furnace}
		\label{tab:nt}
		\resizebox{\textwidth}{!}{
%		\begin{tabular}{rl ll ll}% ll ll ll ll }%ll ll ll ll ll ll ll}
		\begin{tabular}{cc cc cc}% ll ll ll ll }%ll ll ll ll ll ll ll}
			\hline\hline
			Name	&80-150\oc{} [\oc{}/\minutes{}]	&150-200\oc{} [\oc{}/\minutes{}]	&200\oc{}-T$_{\textrm{Cal}}$ [\oc{}/\minutes{}]	&T$_{\textrm{Cal}}$ [\oc{}] &t$_{\textrm{Cal}}$ [\minutes{}]	\\
			\hline
			NT1		&2					&1					&2				&400	&60  \\
			NT2		&2					&2					&2				&400	&60  \\
			NT3		&3					&3					&3				&400	&60  \\
			NT4		&4					&4					&4				&400	&60  \\
			NT5		&4					&4					&4				&500	&60  \\
			NT6		&1					&1					&1				&400	&60  \\
	%		NT7		&max				&max				&max			&600	&60  \\
			\hline\hline
		\end{tabular}
	}
	\end{subtable}
\end{table}
%
%\clearpage
The NT1 heating program was used to mimic the HP1 heating procedure from the heating 
plate in the Naberterm muffle furnace. 
NT2 is an simplification of NT1 and programs NT3~-~NT6 are the same as NT2 with altered 
heating rate and 
NT5 additionally used a calcination temperature T$_{\textrm{Cal}}$ of \SI{500}{\celsius}.
NT2-NT6 had 2 variables (heating rate and one calcination temperature) in contrast to 
NT1 which had 4 (three different heating rates and calcination temperature). 
All heating programs were held at the calcination temperature for one hour.
%In figure \ref{fig:heat} the different heating curves are depicted. 
%
%\begin{figure}
%	\centering
%	\includegraphics[width=.7\textwidth]{../Data/Graphs/hp1.png}
%	\caption{Different heatings curves}
%	\label{fig:heat}
%\end{figure}

@@

The measured I-V curves therefore represent the vertical resistance of the deposited layer. 
This resistance will be predominantly influence by the presence of shunts (hotspots or short-cuts between the top and bottom contact), appearing due to the inhomogenous thickness, and pinholes through the ZrO2 layer.

@@

%$T_{C}$[\oc{}]
%$v_{C}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a C machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see appendix~\ref{sec:app-pre-emma}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The stabilization agent was changed from \gls{acoh} to \gls{ipo} 
shortly before the \gls{pso}
because of much better solution stability and similar electric properties of resulting layers (how did you test this?? see appendix \ref{sec:app-pre-emma}).
The best process after this set of experiments was chosen to be tested with 
\ml{1} \gls{acoh} (sample no.~199), \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} (sample no.~201) and \ml{1} \gls{ipo} (sample no.~192).
%\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
The sample produced with \gls{ipo} as stabilization agent showed comparable electric insulation results (see appendix \ref{sec:app-pre-emma}) and better stability of the solution. 
Therefore, \gls{ipo} was used  as stabilzier in further experiments.
%\td{After the boundaries of the solution were fixed }
After the base recipe for the solution has been decided
the process variables to produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, C velocity and C temperature as input variables.}
See table~\ref{tab:input} for the input space spanned during the optimization.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{zr}$	&$n_L$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}
\fi

>>>>

\section{Substrate Preparation}
Five different substrates were used throughout this work: 
1 mm-thick, soda-lime microscope glass slides 
%\linebreak[4] 
(\cm{2.5}$\times$\cm{7.5}) from Sigma Aldrich, thinner, 
squared glass plates (\cm{2.5}\x\cm{2.5}) Menzel Gläser,
\gls{ito} coated glass (\cm{2.5}\x\cm{2.5}) from Sigma Aldrich with a sheet resistance of approximately 12 $\Omega$/sq, 
\gls{fto} coated glass (\cm{5}\x\cm{5}) from Sigma Aldrich and steel foil (10~cm~x~10~cm) provided by Sunplugged GmbH (\url{http://sunplugged.at/)}.
%
The steel foil was cut with a foil cutter into \cm{2.5}\x\cm{2.5} squares.
Glass was used because of its low price point and availability and to measure transmission and reflectance spectra. 
\Gls{fto} and \gls{ito} coated conducting substrates were used for \gls{sem} investigation and for electrical measurements (serving as one of the electrical contacts).
%\gls{fto} and \gls{ito} were used in order to have a conducting substrate. 
%, which is needed to measure the conductivity of the applied layer and \td{for \gls{sem} micrographs. (don't follow?)}
The conducting substrate allows for easy measurement of electric conductance in vertical direction.
Furthermore, while taking a \gls{sem} micrograph the sample would quickly accumulate negative charge and repel further electrons without a conducting substrate.
%The glass slides and \gls{fto} were scored with a diamond scribe \ds{\td{(diamond scratcher/scraper)} }and broken with a running plier into pieces of dimensions \cm{2.5}\x\cm{2.5}.
%The steel foil was cut with a foil cutter into squares of the same dimensions. 
%, a cutter knife (repeatedly), a paper cutter or a scissors (ordered by increasing curvature of resulting plates).
All substrates were cleaned in three steps before usage:
\begin{enumerate}
	\item \minutes{15} in \ml{50} \gls{water} and \ml{1} of Hellmanex III alkaline concentrate in an ultrasonic bath
	\item \minutes{15} in \gls{water} in an ultrasonic bath
	\item \minutes{15} in \gls{ipo} in an ultrasonic bath 
\end{enumerate}
%\td{is that the usual procedure for steel?}
After the last cleaning step, the samples were blown dry with dry \gls{n2} gas and kept in a clean plastic container until the coating step (cf. \cite{YAMASHITA2018,Kohli2010}).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Aqueous Precursor Solutions}
\label{sec:exp-sol-aq}
\gls{zrpro} was added to acetylacetone (\gls{acac}) while stirring and in a separate vessel \gls{water} 
(including any optional additives such as \gls{sds}, \gls{hcl}, \gls{h2so4} or \gls{naoh}) 
was added to isopropyl alcohol (\gls{ipo}) and both were stirred for one hour. 
These additives were added to influence pH and surface tension with the goal to influence the homogeneity of the resulting layer. %(in terms of what?)}. % \td{see Parvulescu2015}
The \gls{water}-\gls{ipo} mixture was added to the \gls{zrpro}-\gls{acac} solution and stirred over night. 
The exact volumes can be taken from table~\ref{tab:rec1}.
%Unfortunately, this solution failed to produce \td{anything near homogeneous layers (??)}.
Unfortunately, this solution failed to produce homogeneous layers, but instead only resulted in sparse patches of deposits on the substrate.
Thus, an alternative solution was found.
%\td{At this point in time everything was doctor bladed by hand. The hight was varied (with tape).}
\begin{table}[h]
	\centering
	\caption{Compositions of different aqueous solutions}
	\label{tab:rec1}
	\begin{tabular}{llllllll}
		\hline
		recipe				&1		&2		&3		&4		&5		&6		&7\\
		\hline
		\gls{zrpro} [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{acac}  [\ml{}]	&8		&8		&8		&8		&8		&8		&8\\
		\gls{ipo}   [\ml{}]	&2		&2		&2		&2		&2		&2		&2\\
		\gls{water} [\ml{}]	&2.6	&2.6	&2.5	&2~		&2		&2		&2\\
		\gls{sds}   [\mg{}]	&-		&5.9	&-		&-		&-		&-		&-\\
		\gls{hcl}   [\ml{}]	&-		&-		&-		&-		&0.5	&-		&-\\
		\gls{h2so4} [\ml{}]	&-		&-		&-		&-		&-		&0.5	&-\\
		\gls{naoh}  [\ml{}] &-		&-		&-		&-		&-		&-		&0.5\\
		\hline
	\end{tabular}
\end{table}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Buthanolic Solution}\label{sec:exp-sol-bu}
%\todo{what did you did you do percisely! It must be logical and should be followed}
Five different concentrations of the buthanolic solutions were prepared.
\ds{
\td{Not all (which?)} chemicals mentioned by Hu~et~al.\cite{Hu2016} were available, so chemically similar 
starting materials had to be chosen from the available inventory. 
}
The base recipe (\gls{1f}) was inspired by Hu~et~al.\cite{Hu2016}.
\Gls{buoh}, \gls{zrpro}, \gls{acac} and \gls{ipo}/\gls{acoh} were used as solvent, precursor, chelating agent and stabilization agent, respectively.

@@

\begin{table}[h]
	\centering
    \caption{Heating programs}
	\label{tab:heating}
	\begin{subtable}{\textwidth}
		\centering
		\subcaption{Heating program HP1 used with the Labtech EH45C heating plate}
		\label{tab:labtech}
%		\begin{tabular}{rl ll ll ll ll ll ll }%ll ll ll ll ll ll ll}
		\begin{tabular}{cc cc cc cc cc cc cc }%ll ll ll ll ll ll ll}
			\hline
			\hline
			T [\oc{}]	    &80		&100	&150	&160	&170 	&180	&190	&200	&250	&300	&350	&400	\\
			\hline
			t [\minutes{}]	&10 	&10		&5 		&5 		&5 		&5 &5 &10 &10 &10 &10 &60 \\
			\hline
			\hline
		\end{tabular}
	\end{subtable}
%%%%%%%%%%%%
	\begin{subtable}{\textwidth}
		\centering
		\subcaption{Heating programs NT1 - NT6 used with the Naberterm LB410 muffle furnace}
		\label{tab:nt}
		\resizebox{\textwidth}{!}{
%		\begin{tabular}{rl ll ll}% ll ll ll ll }%ll ll ll ll ll ll ll}
		\begin{tabular}{cc cc cc}% ll ll ll ll }%ll ll ll ll ll ll ll}
			\hline\hline
			Name	&80-150\oc{} [\oc{}/\minutes{}]	&150-200\oc{} [\oc{}/\minutes{}]	&200\oc{}-T$_{\textrm{Cal}}$ [\oc{}/\minutes{}]	&T$_{\textrm{Cal}}$ [\oc{}] &t$_{\textrm{Cal}}$ [\minutes{}]	\\
			\hline
			NT1		&2					&1					&2				&400	&60  \\
			NT2		&2					&2					&2				&400	&60  \\
			NT3		&3					&3					&3				&400	&60  \\
			NT4		&4					&4					&4				&400	&60  \\
			NT5		&4					&4					&4				&500	&60  \\
			NT6		&1					&1					&1				&400	&60  \\
	%		NT7		&max				&max				&max			&600	&60  \\
			\hline\hline
		\end{tabular}
	}
	\end{subtable}
\end{table}
%
%\clearpage
The NT1 heating program was used to mimic the HP1 heating procedure from the heating 
plate in the Naberterm muffle furnace. 
NT2 is a simplification of NT1 and programs NT3~-~NT6 are the same as NT2 with altered 
heating rate and 
NT5 additionally used a calcination temperature T$_{\textrm{Cal}}$ of \SI{500}{\celsius}.
NT2-NT6 had 2 variables (heating rate and one calcination temperature) in contrast to 
NT1 which had 4 (three different heating rates and calcination temperature). 
All heating programs were held at the calcination temperature for one hour.
%In figure \ref{fig:heat} the different heating curves are depicted. 
%
%\begin{figure}
%	\centering
%	\includegraphics[width=.7\textwidth]{../Data/Graphs/hp1.png}
%	\caption{Different heatings curves}
%	\label{fig:heat}
%\end{figure}

@@

The measured I-V curves therefore represent the vertical resistance of the deposited layer. 
This resistance will be predominantly influence by the presence of shunts (hotspots or short-cuts between the top and bottom contact), appearing due to the inhomogeneous thickness, and pinholes through the ZrO2 layer.

@@

%$T_{C}$[\oc{}]
%$v_{C}$[\mm{}/\s{}]
%$T_{cal}$[\oc{}]
%$v_{cal}$[\oc{}/\h{}]
%Especially the doctor blading velocity.
%}
%It was tried to reduce the waiting time and the resulting \td{drying stains}
%by using a heat gun. The drying was
%accelerated but not reproducibly and the glass plate on the film applicator was changed 
%against the heatable plate.
%With this new buthanolic recipe and heatable plate the limits of the optimization problem 
%were explored in a preliminary study using the Plackett-Burman \cite{Plackett1946} design 
%implemented in the \texttt{python3} library \texttt{pyDOE}.
%For the preliminary study a C machine and NT were used and the steel. 
\ds{In the preliminary study only steel was used as substrate.}
%The Plackett-Burman \cite{Plackett1946} design implemented in the python3 library \texttt{pyDOE} was used to
%get an overview of reasonable boundaries.
%Latin squares were used to chose which experiments should be ausgefuehrt to get an ueberblick of the optimization room.
%See Code/Input_DOE/make_*exps.py and Code/Input_DOE/mail_theo
Some additional hand picked experiments (see appendix~\ref{sec:app-pre-emma}) were introduced to further narrow down the limits of 
the optimization as every reduction in variables or levels meant a faster convergence.
%ooooh 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The stabilization agent was changed from \gls{acoh} to \gls{ipo} 
shortly before the \gls{pso}
because of much better solution stability and similar electric properties of resulting layers (see samples 192, 199 and 201 in appendix \ref{sec:app-pre-emma}).
The best process variables up to this point were chosen to be tested with 
\ml{1} \gls{acoh} (sample no.~199), \ml{0.5} \gls{acoh} plus \ml{0.5} \gls{ipo} (sample no.~201) and \ml{1} \gls{ipo} (sample no.~192).
%\td{As the sample showed the best all ex were proceeded with ipo as stabilization agent. }
The sample produced with \gls{ipo} as stabilization agent showed comparable electric insulation results (see appendix \ref{sec:app-pre-emma}) and better stability of the solution. 
Therefore, \gls{ipo} was used  as stabilizer in further experiments.
%\td{After the boundaries of the solution were fixed }
After the base recipe for the solution has been decided
the process variables to produce an insulating layer was examined. 
%There were many variables which had to be taken into account. 
%\td{plachett-burman design of experiment with conc, layers, calcination temperature, heating rate, C velocity and C temperature as input variables.}
See table~\ref{tab:input} for the input space spanned during the optimization.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\iffalse
\begin{table}[ht!]
	\centering
	\caption{Final values used in the \gls{pso}.}
    \label{tab:space}
    \begin{tabular}{cccccc}
        \hline\hline
		$c_{zr}$	&$n_L$	&$v_{C}$	&$T_{C}$	&$v_{cal}$	&$T_{cal}$		\\
%        concentration   &layers &\gls{db} velocity  &\gls{db} temperature   &heating rate   &calcination temperature    \\
        \hline
        2   &4  &10 &40 &120    &300    \\
        3   &6  &12 &50 &360    &400    \\
        4   &8  &14 &60 &600    &500    \\
        5   &10 &16 &70 &840    &       \\
            &12 &18 &80 &1080   &       \\
            &   &20 &   &       &       \\
        \hline\hline
    \end{tabular}
\end{table}
\fi

### 2024-08-11 doc/Thesis/chapter/050-results-material.tex
correct misspellings

The sol-gel recipe reported by Hu et al.\cite{Hu2016} and further optimzed, led to improved results (see section~\ref{sec:exp-sol-bu}). 
%
Figure~\ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic solution on top of a steel substrate. 
%%%% PIN HOLES
The large irregularity on the bottom left could depict a pin hole, a hole in the layer that reaches to the substrate. 
These irregularities are rather the exception. 
Alternatively, the small, hardly visible cracks spread across the surface could depict such pin holes. 
% These - I think - are rather only one layer deep irregularities since they are so prevalent and hardly any pin holes were electrically observed on similar samples. \todo{where is the evidence?}

%%%%%% STABILITY
As soon as the solution showed initial cloudiness, it was declared as unstable and used no more for \gls{db}. %\td{(coating! DB = deutsche Bahn ... ist mir schon vorher aufgefallen)}
The solution becoming opaque indicated build-up of precipitation and was not further used.
The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent \gls{acoh} with \gls{ipo}.
A \gls{1f} and a \gls{4f} solution with \gls{acoh} - sealed with Parafilm - was stable for approximately \h{24} and \h{2}, respectively.
%192 was first with IPOH
Whereas a \gls{4f} solution with \gls{ipo} as stabilizing agent stayed stable for circa \h{96}. 
An increase of the \gls{zrpro} concentration accelerates the aging process of the solution.
%\td{what is this aging process chemically? oxidation, hydrolization?}.
The aging process was accelerated by absence of proper sealing.
\td{The aging process dependends on the water in the air corresponding to an hyrolization process\cite{Hu2016}.}
%
The introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
as they could be stored until the next day, instead of producing a new, separate solution for each day.
%
It was found that after a \gls{4f} \gls{acoh} solution has 
%aged beyond cloudiness 
shown precipitation (became opaque)
the addition 50\% of the volume in \gls{ipo} can even reverse the aging effect for a respectable amount of time. 
This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
even after 5 fold dilution. 
%Whereas addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect. 
%Whereas, when the addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect.

>>>>

The sol-gel recipe reported by Hu et al.\cite{Hu2016} and further optimized, led to improved results (see section~\ref{sec:exp-sol-bu}). 
%
Figure~\ref{fig:sem-ph} shows a top view of 10 layers of the buthanolic solution on top of a steel substrate. 
%%%% PIN HOLES
The large irregularity on the bottom left could depict a pin hole, a hole in the layer that reaches to the substrate. 
These irregularities are rather the exception. 
Alternatively, the small, hardly visible cracks spread across the surface could depict such pin holes. 
% These - I think - are rather only one layer deep irregularities since they are so prevalent and hardly any pin holes were electrically observed on similar samples. \todo{where is the evidence?}

%%%%%% STABILITY
As soon as the solution showed initial cloudiness, it was declared as unstable and used no more for \gls{db}. %\td{(coating! DB = deutsche Bahn ... ist mir schon vorher aufgefallen)}
The solution becoming opaque indicated build-up of precipitation and was not further used.
The visually asserted stability of the solution could be increased a lot by replacing the stabilizing agent \gls{acoh} with \gls{ipo}.
A \gls{1f} and a \gls{4f} solution with \gls{acoh} - sealed with Parafilm - was stable for approximately \h{24} and \h{2}, respectively.
%192 was first with IPOH
Whereas a \gls{4f} solution with \gls{ipo} as stabilizing agent stayed stable for circa \h{96}. 
An increase of the \gls{zrpro} concentration accelerates the aging process of the solution.
%\td{what is this aging process chemically? oxidation, hydrolization?}.
The aging process was accelerated by absence of proper sealing.
The aging process depends on the water in the air corresponding to an hydrolization process\cite{Hu2016}.
%
The introduction of \gls{ipo} into the recipe allowed higher concentrated solutions to be practicable 
as they could be stored until the next day, instead of producing a new, separate solution for each day.
%
It was found that after a \gls{4f} \gls{acoh} solution has 
%aged beyond cloudiness 
shown precipitation (became opaque)
the addition 50\% of the volume in \gls{ipo} can even reverse the aging effect for a respectable amount of time. 
This effect is not only due to dilution as additional solvent (\gls{buoh}) did not re-stabilize the solution, 
even after 5 fold dilution. 
%Whereas addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect. 
%Whereas, when the addition of the original stabilizing agent \gls{buoh} to an aged solution had no effect.
